### 2015-03-15 staticanalysis.tex
updates in summarisation

>>>>

Early on during the development of \whoop we realised that scalability would be a serious issue. When we tried to apply \whoop on the r8169 RealTek ethernet driver (8000 lines of C code), we were running out of memory. One reason was that the translation produced hundreds of thousands of Boogie IVL code, which were slow to parse and fit in memory. Another reason was that some entry points of the driver recursively call helper functions. Inherently, recursion does not work with inlining.

To tackle the above issues we developed \emph{watchdog summarisation}, a novel summarisation technique that allows us to analyse Linux kernel modules in a scalable fashion, but without destroying precision and reporting countless false positives. Watchdog summarisation combines watchdog race checking with pre- and post-conditions and loop invariants for increased precision.

Kernel imposed locks
Sound reduction of checked memory regions
Modelling kernel methods
Controlling SMACK's coarse over-approximation of function pointers
